### 2019-06-25 papers/journal/conclusion.tex
Minor Update

\noindent 
We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate
into a global, observable properties of the VTS. 
%
Interactions between SNARE proteins and their
regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological
properties of the transport graph; all VTSs based on v-SNARE t-SNARE interactions must be 2-strongly connected.
% 
Additionally, we demonstrate how we can aid in predicting new vesicles given an incomplete VTS as input. 
%
Our approach demonstrates the power of SMT solvers in a novel application and the value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool up
to the size that makes the tool biologically relevant.
%To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%%
%The constraints implied by SNARE protein properties translates into
%mathematically elegant properties of the transport graph, namely its connectivity.
%%
%Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
%We manage to scale the tool up to the size that makes the tool biologically relevant.
%

>>>>

\noindent 
We demonstrate in our work how local regulatory interactions between molecules of the VTS, translate
into a global, observable properties of the VTS. 
%
Interactions between SNARE proteins and their
regulators, which in its simplest form can be encoded in a pairing matrix, constrain the topological
properties of the transport graph; all VTSs based on V-SNARE T-SNARE interactions must be 2-strongly connected.
% 
Additionally, we demonstrate how we can aid in predicting new vesicles given an incomplete VTS as input. 
%
Our approach demonstrates the power of SMT solvers in a novel application and the value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool up
to the size that makes the tool biologically relevant.
%To conclude, we have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%%
%The constraints implied by SNARE protein properties translates into
%mathematically elegant properties of the transport graph, namely its connectivity.
%%
%Our approach demonstrates the power of SMT solvers in a {\em novel} application and the value of careful encoding of the problems into SMT queries. 
%We manage to scale the tool up to the size that makes the tool biologically relevant.
%
